### 2025-05-05 chapters/1-qcd.tex
Pre-correction version of thesis

% -----------------------------------
% Particles Section:
% -----------------------------------
\begin{sourcefigure}[t!]
    % Figure graphics
    \centering
    \includegraphics[width=\textwidth]{example-image-a}

    % Caption
    \caption[A cartoon of the ideas of renormaliztion, in the context of zooming in from the largest to the smallest scales of the universe.]{
        A cartoon depicting zooming in on the universe, beginning at the largest known scales and ending at some of the smallest -- the scales of \gls{qcd}.
        %
        The top row, from right to left, depicts galactic filaments, galaxies, and the solar system.
        %
        The middle row depicts terrestrial scales (right to left):
        %
        the earth, a hunk of iron, the magnetic domains within iron, and a single iron atom.
        %
        The bottom row depicts the scales of \gls{qcd} (right to left):
        %
        a proton, a jet, a partonic splitting, and a single quark.
    }
    % Figure Label
    \label{fig:picturebook_universe}
\end{sourcefigure}

@@

% -----------------------------------
% Substructure Section:
% -----------------------------------
\begin{sourcefigure}[t!]
    % Figure graphics
    \centering
    \includegraphics[width=0.8\textwidth]{figures/picturebook/jet-contamination}

    % Caption
    \caption[A visualization of the low-energy contamination within jets, whose removal is the goal of jet grooming.]{
        The goal of \emph{jet grooming} is to recover the information of high-energy jet substructure representing the physics of high energy quarks and gluons (visualized as dark, opaque lines, with darker colors/more opacity indicating higher energy) despite obfuscation from soft distortions (hadronization, detector effects) and additive contamination (pileup, underlying event).
    }

@@

    % Caption
    \caption[A visualization of energy-weighted correlations capturing correlations between different high-energy structures within jets at different scales. \sam{incomplete, want bunch crossings rather than nuclei}]{
        Energy-weighted correlators capture correlations between high-energy structures within jets, such as particles (purple/black lines) or subjets (purple cones).
        %
        The explicit example of the resolved 3-point energy correlators of \Chap{ewocs}, compute using real collider data, are shown as colored disks above the jet to visualize energy-weighted correlations at different angular scales.
        %
        The higher energy regions of the cartoon jet depicted here are represented by higher values of the associated resolved energy correlator, and darker colors in the associated colored disks.
        %
        \sam{incomplete, want bunch crossings rather than nuclei}
    }
    % Figure Label
    \label{fig:picturebook_eventshapes}
\end{sourcefigure}

@@

70 years ago, humanity discovered new particles that nobody expected.
%
We had only the brilliant minds of humanity's experimental and theoretical physicists to battle against the looming darkness of incomprehension.
%
The triumph of these physicists in the theory of \gls{qcd} has led to a rich new story of quarks, gluons, and the inner structure of jets.
%
Thanks to their effort, and that of their successors, we now have methods to piece together the properties of the smallest known constituents of 99.9\% of the visible mass of our universe from high-energy particle collisions, even through the ubiquitous haze of contaminating pollution that obfuscate scattering events.
%
I hope to lucidly convey a small piece of this story.

>>>>

% -----------------------------------
% Particles Section:
% -----------------------------------
\begin{sourcefigure}[t!]
    % Figure graphics
    \vspace{-20pt}

    \hspace{-35pt}
    \includegraphics[width=1.2\textwidth]{figures/misc/renormalization.pdf}

    % Caption
    \caption[A cartoon of the idea of renormalization, in the context of zooming in from the largest to the smallest scales of the universe.]{
        A depiction of the concepts of renormalization via zooming in on the universe.
        %
        The top row, from right to left, depicts (simulated) galactic filaments \cite{illustrisTNG}, (simulated) galaxy superclusters \cite{illustrisTNG}, a milkyway-like galaxy \cite{eso}, and the solar system \cite{natgeo}.
        %
        The middle row depicts terrestrial scales:
        %
        the earth \cite{nasa}, a slab of banded iron \cite{usgs}, magnetic domains modelled by the Ising model \cite{Sitarachu_2022}, and a visualization of a single iron atom \cite{iron_stock}.
        %
        The bottom row depicts visualizations of the scales of \gls{qcd}:
        %
        a proton, a jet, a single partonic splitting, and a single free quark.
    }
    % Figure Label
    \label{fig:picturebook_universe}
\end{sourcefigure}

@@

% -----------------------------------
% Substructure Section:
% -----------------------------------
\begin{sourcefigure}[t!]
    % Figure graphics
    \centering
    \includegraphics[width=0.8\textwidth]{figures/picturebook/pu-jet}

    % Caption
    \caption[A visualization of the low-energy contamination within jets, whose removal is the goal of jet grooming.]{
        The goal of \emph{jet grooming} is to recover the information of high-energy jet substructure representing the physics of high energy quarks and gluons (visualized as dark, opaque lines, with darker colors/more opacity indicating higher energy) despite obfuscation from soft distortions (hadronization and detector effects) and additive contamination (pileup, depicted in the figure, and the underlying event).
    }

@@

    % Caption
    \caption[A visualization of energy-weighted correlations capturing correlations between different high-energy structures within jets at different scales.]{
        Energy-weighted correlators capture correlations between high-energy structures within jets, such as particles (purple/black lines) or subjets (purple cones).
        %
        The explicit example of the resolved 3-point energy correlators of \Chap{ewocs}, compute using real collider data, are shown as colored disks above the jet to visualize energy-weighted correlations at different angular scales.
        %
        The higher energy regions of the cartoon jet depicted here are represented by higher values of the associated resolved energy correlator, and darker colors in the associated colored disks.
    }
    % Figure Label
    \label{fig:picturebook_eventshapes}
\end{sourcefigure}

@@

70 years ago, humanity discovered new particles that nobody expected.
%
We had only the brilliant minds of humanity's experimental and theoretical physicists to battle against the looming darkness of incomprehension.
%
The triumph of these physicists in the theory of \gls{qcd} has led to a rich new story of quarks, gluons, and the inner structure of jets.
%
Thanks to their effort, and that of their successors, we now have methods to piece together the properties of the smallest known constituents of 99.9\% of the visible mass of our universe from high-energy particle collisions, even through a ubiquitous haze of contaminating pollution that obfuscate scattering events.
%
I hope to lucidly convey a small piece of this story.
